On the goodness-of-fit of an exponential random graph model to a social network sample

### 2021-01-20 Manuscript/manuscript.tex
Updated table reference

The complexity factor is finally examined by varying the complexity of the exponential random graph model (ERGM) that is applied to the different network samples. Note that a complexity continuum has already defined by way of the network samples which vary in their size and heterogeneity. ERGMs with low, moderate, and high respective complexity are fitted to each of these different samples. As such, with regards to the heterogeneity factor, three different scenario's are identified. It is consequently examined whether the precision of the meta-analyzed ERGM increases for a decrease in the discrepancy between sample and model complexity. It is also assessed whether this is consistent with the goodness-of-fit (GOF) indices. Furthermore, both covariate and structural effects are included in each ERGM, which remain constant regardless of the complexity of the sample to which the ERGM is applied. This enables examining whether covariate parameters estimates are more precise than their structural counterparts. \clearpage \noindent The reader is referred to table 1 for a more concise overview of the set-up of the simulation study. As becomes apparent from the table, in total $27$  simulation scenario's can be be identified.

@@

>>>>

The complexity factor is finally examined by varying the complexity of the exponential random graph model (ERGM) that is applied to the different network samples. Note that a complexity continuum has already defined by way of the network samples which vary in their size and heterogeneity. ERGMs with low, moderate, and high respective complexity are fitted to each of these different samples. As such, with regards to the heterogeneity factor, three different scenario's are identified. It is consequently examined whether the precision of the meta-analyzed ERGM increases for a decrease in the discrepancy between sample and model complexity. It is also assessed whether this is consistent with the goodness-of-fit (GOF) indices. Furthermore, both covariate and structural effects are included in each ERGM, which remain constant regardless of the complexity of the sample to which the ERGM is applied. This enables examining whether covariate parameters estimates are more precise than their structural counterparts. \clearpage \noindent The reader is referred to table \ref{table:table1} for a more concise overview of the set-up of the simulation study. As becomes apparent from the table, a total of $27$  simulation scenario's can be be identified.

@@

\label{table:table1}
